---
title: "Untitled"
output: html_document
date: "2022-10-03"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(naniar)
library(gapminder)
```

## Notes about p-hacking

## Introducing the tidyverse

We always load our package at the top of the Rmd document.

### msleep

```{r}
msleep
```

Let's look at a data.frame

```{r}
class(quakes)
```

Let's use select to get some columns from msleep

```{r}
select(msleep, name, sleep_total)
```

We can use "tidy selection" functions to help us select columns

```{r}
select(msleep, name, starts_with("sleep"))
```

If we want to **pull** out a column as a vector we use pull()

```{r}
pull(msleep, name)
```

#### count()

```{r}
count(msleep, vore)
```

Let's write this with the pipe:

```{r}
msleep %>% 
  count(vore)
```

A simpler pipe

```{r}
"cats" %>% 
  rep(5)
```

... without the pipe

```{r}
rep("cats", 5)
```

Can you tell me what this will make (without running it!)

```{r}
"cats" %>% 
  paste("are great")
```

... but sometimes we see more complicated pipes with a .

```{r}
"cats" %>% 
  paste(., "are great but one can have too many", .)
```

... count() can do hierarchical counting!

```{r}
msleep %>% 
  count(conservation, vore, sort = TRUE)
```

#### filter()

```{r}
msleep %>% 
  filter(vore == "carni") %>% 
  select(name)
```

We negate a condition with a !

```{r}
msleep %>% 
  filter(vore != "carni") %>% 
  select(name)
```

How about missing values? In R they are called NA. We CANNOT use a condition to filter them, we need to use is.na()

```{r}
msleep %>% 
  filter(is.na(sleep_rem))
```

REMEMBER TO LOAD {naniar} AT THE TOP OF THE RMD!

```{r}
msleep %>% 
  gg_miss_upset()
```

#### ggplot2!

Let's start our chart

```{r}
msleep %>% 
  ggplot() + 
  aes(x = sleep_rem,
      y = sleep_total) +
  geom_point()
```

Copy the chart above so we build it up slowly!!

```{r}
msleep %>% 
  ggplot() + 
  aes(x = sleep_rem,
      y = sleep_total,
      colour = vore) +
  geom_point() + 
  labs(x = "Hours in REM",
       y = "Total hours slept",
       title = "REM cycles in mammals")
```

### msleep mean sleep

Calculate mean sleep time per diet. Need group_by()

```{r}
mean_sleep_by_vore <- msleep %>%
  group_by(vore) %>% 
  summarise(mean_sleep_total = mean(sleep_total)) %>% 
  ungroup()
```

```{r}
mean_sleep_by_vore %>% 
  ggplot() + 
  aes(y = vore,
      x = mean_sleep_total) +
  geom_col()
```

### mutating multiple columns at once

```{r}
msleep %>% 
  mutate(across(starts_with("sleep"),
                ~ . / 24))
```

# Gapminder!

Remember - load packages AT THE TOP.

```{r}
gapminder %>% 
  filter(year == 2007) %>% 
  ggplot() +
  aes(x = lifeExp,
      y = gdpPercap,
      colour = continent) +
  geom_point()
```

# Global Burden of Disease

```{r}
gbd_data <- read_csv("data/global-burden-of-disease-data.csv")
```

```{r}
wb_death_causes_2019 <- gbd_data %>% 
  filter(str_starts(location_name, "World Bank")) %>% 
  filter(year == max(year)) %>% 
  filter(metric_name == "Percent") %>% 
  filter(cause_name != "All causes") %>% 
  select(location_name, cause_name, val)
```

```{r}
wb_death_causes_2019 %>% 
  ggplot() +
  aes(x = val,
      y = location_name,
      fill = cause_name) +
  geom_col() +
  theme(legend.position = "top")
```



