---
title: "Untitled"
output: bookdown::html_document2
date: "2022-11-28"
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gt)
library(ggtext)
```

Let's reference that paper @ahn_flavor_2011-1 AND ANOTHER GOOD PAPER @viet_data-driven_2020

# Another chart

I need to

- change colours!
- use fct_relevel()
- position of NA

## Change all colours

```{r}
msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(fill = "forestgreen")
```

If you want a "darker" version of a colour we can use the {colorspace} package

```{r}
msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(fill = colorspace::darken("forestgreen"))
```

## Change colours manually

```{r}
msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE) +
  scale_fill_manual(values = c("herbi" = "forestgreen",
                               "carni" = "red"))
```

## using a custom order with fct_relevel

```{r}
order_vore_by_meat <- c("carni", "omni", "insecti", "herbi")

msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_relevel(vore, order_vore_by_meat),
         vore = fct_rev(vore)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE)
```

## Moving around NA

We need to stop and think.

To put NA into an ordered position, easiest way is with fct_explicit_na()

```{r}
msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_explicit_na(vore, "Unknown diet"),
         vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE)
```

Moving NA to a specific position

```{r}
order_vore_by_meat <- c("carni", "omni", "insecti", "herbi")

msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_relevel(vore, order_vore_by_meat),
         vore = fct_rev(vore),
         vore = fct_explicit_na(vore, "Unknown diet"),
         vore = fct_relevel(vore, "Unknown diet", after = 0)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE)
```

# Tables

```{r}
msleep %>% 
  count(vore) %>% 
  arrange(desc(n)) %>% 
  gt() %>% 
  cols_label(vore = "Diet",
             n = "Count")
```

## ggtext!

1. Load the {ggtext} package!
2. We need to make our title, let's write it outside of a code chunk first

Most animals are <span>herbivores</span>

Most animals are <span style='color:#228B22'>herbivores</span>

3. Tell the theme you're using HTML with element_markdown()

```{r}
msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE) +
  scale_fill_manual(values = c("herbi" = "forestgreen",
                               "carni" = "red",
                               "omni" = "yellow",
                               "insecti" = "blue")) +
  labs(title = "Most animals are <span style='color:#228B22'>herbivores</span>",
       caption = "By Charlotte @charliejhadley") +
  theme(plot.title = element_markdown(),
        plot.title.position = "plot")
```

# Captions...

Do we want the caption in the chart or "in the report"?

```{r, fig.cap="This chart demonstrates things"}
msleep %>% 
  count(vore) %>% 
  mutate(vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE) +
  scale_fill_manual(values = c("herbi" = "forestgreen",
                               "carni" = "red",
                               "omni" = "yellow",
                               "insecti" = "blue")) +
  labs(title = "Most animals are <span style='color:#228B22'>herbivores</span>") +
  theme(plot.title = element_markdown(),
        plot.title.position = "plot")
```

## 2nd assessment chart question

```{r}
msleep %>% 
  count(conservation, vore) %>% 
  mutate(vore = fct_reorder(vore, n)) %>% 
  ggplot() +
  aes(x = n,
      y = vore) +
  geom_col(aes(fill = vore),
           show.legend = FALSE) +
  scale_fill_manual(values = c("herbi" = "forestgreen",
                               "carni" = "red",
                               "omni" = "yellow",
                               "insecti" = "blue")) +
  facet_wrap(~ conservation)
```



```{r}
ggplot() +
  aes(x = c(1,2,4),
      y = 4) +
  geom_point()
```



