---
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

# Global Burden of Disease (GBD) study

Register for this tool here. I've downloaded an example series of data

```{r}
library(tidyverse)
library(janitor)
library(here)

disease_burden_raw <- read_csv(here("static", "datasets", "data-example_global-burden-of-disease", "data-example_global-burden-of-disease.csv"))

disease_burden_raw %>% 
  count(location_name)
```

# Gapminder

It's the gapminder dataset!

# Western Collaborative Group Study

> "Explore the relationship between systolic blood pressire (sbp) and personality types (personality_2L), accounting for potential confounders like weight (weight)"
> R for Health Data Science, Ewn Harrison and Riinu Pius page 173

- Used for regression

```{r}
finalfit::wcgs %>% 
  as_tibble()
```

# Survival from Malignant Melanoma

> "Association between tumour ulceration and death from melanoma"
> R for Health Data Science, Ewn Harrison and Riinu Pius page 194

Data is numerically coded, needs to be converted to meaningful factor levels. Used for cox-model

```{r}
boot::melanoma
```

# colon_s data

> "association between cancer obstructing the bowel and 5-year survival, accounting for other patient and disease characteristics"
> R for Health Data Science, Ewn Harrison and Riinu Pius page 194

- Used for missing data identification

```{r}
finalfit::colon_s %>% 
  as_tibble()
```

# A hypothesis is a liability

doi.org/10.1186/s13059-020-02133-w

```{r}
read_table(here::here("static", "datasets", "hypothesis-dataset/data9b_m.txt"))
```

# Survey datasets

## British Election Study

Found from https://twitter.com/PollsAndVotes/status/1566803528911298561?s=20&t=hL3RLFYrUfMSPr4w0kQ9sw

THIS TAKES SOME EXPLAINING!

I was initially linked to this page: https://www.britishelectionstudy.com/data-object/2019-british-election-study-post-election-random-probability-survey/ and I needed an account to download these files. Now. If instead we went to the UK Data Service http://doi.org/10.5255/UKDA-SN-8875-1 and click through to the UK Data Service catalogue page (https://beta.ukdataservice.ac.uk/datacatalogue/studies/study?id=8875) we can then register to download the dataset officially.

Included in this download is a data dictionary stored in an .RTF file. Which is a mess and not nice.
 
Directly from the Study website I downloaded these files:

- SPSS file: .sav
- Stata file: .dta
- Questionnaire PDF
- Explanatory Notes

Both these files have coded column names. Each of these columns contain two pieces of information:

- label which contains the question text
- labels which contains the question response values

```{r}
library(haven)
british_election_study_spss <- read_sav(here::here("static", "datasets", "british-election-study/bes_rps_2019_1.1.1.sav"))
british_election_study_stata <- read_stata(here::here("static", "datasets", "british-election-study/bes_rps_2019_1.1.1.dta"))
```

Get survey questions:

```{r}
bse_questions <- british_election_study_spss %>%
  map_chr(attr_getter("label")) %>%
  enframe()
```

Convert labelled columns to factors:

```{r}
british_election_study_spss %>% 
  select(1:10) %>% 
  mutate(across(where(is.labelled), ~as_factor(.x)))
```

### Task

```{r}
qs_contact_type <- bse_questions %>% 
  filter(str_starts(name, "k14_")) %>% 
  mutate(political_party = str_extract(value, "by .*:"),
         political_party = str_remove(political_party, "by "),
         political_party = str_remove(political_party, ":")) %>% 
  mutate(contact_type = str_remove(value, "Contacted .*:"),
         contact_type = str_trim(contact_type)) %>% 
  select(name, political_party, contact_type)

qs_contact_type

```


```{r}
bse_contacted_by_parties <- british_election_study_spss %>% 
  select(matches("k14_[0-9]")) %>% 
  mutate(across(where(is.labelled), ~as_factor(.x))) %>% 
  pivot_longer(everything()) %>% 
  left_join(qs_contact_type)

bse_contacted_by_parties %>% 
  count(political_party, contact_type, value) %>% 
  drop_na(value) %>% 
  filter(contact_type != "None") %>% 
  group_by(political_party, contact_type) %>% 
  mutate(perc = n / sum(n)) %>%
  ungroup() %>% 
  ggplot(aes(x = perc,
             y = contact_type,
             fill = value)) +
  geom_col() +
  facet_wrap(~ political_party) +
  scale_x_continuous(labels = scales::label_percent())
```

```{r}
british_election_study_spss %>% 
  select(where(is.character))

british_election_study_spss %>% 
  select(k04) %>% 
  filter(str_detect(k04, ",")) %>% 
  mutate(respondent_id = row_number()) %>% 
  separate_rows(k04, 
                sep = ",") %>%
  mutate(k04 = str_trim(k04)) %>% 
  count(k04, sort = TRUE)


bse_questions %>% 
  filter(name == "k04")
```




