---
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

# Global Burden of Disease (GBD) study

Register for this tool here. I've downloaded an example series of data

```{r}
library(tidyverse)
library(janitor)
library(here)

disease_burden_raw <- read_csv(here("static", "datasets", "data-example_global-burden-of-disease", "data-example_global-burden-of-disease.csv"))

disease_burden_raw %>% 
  count(location_name)
```

# Gapminder

It's the gapminder dataset!

# Western Collaborative Group Study

> "Explore the relationship between systolic blood pressire (sbp) and personality types (personality_2L), accounting for potential confounders like weight (weight)"
> R for Health Data Science, Ewn Harrison and Riinu Pius page 173

- Used for regression

```{r}
finalfit::wcgs %>% 
  as_tibble()
```

# Survival from Malignant Melanoma

> "Association between tumour ulceration and death from melanoma"
> R for Health Data Science, Ewn Harrison and Riinu Pius page 194

Data is numerically coded, needs to be converted to meaningful factor levels. Used for cox-model

```{r}
boot::melanoma
```

# colon_s data

> "association between cancer obstructing the bowel and 5-year survival, accounting for other patient and disease characteristics"
> R for Health Data Science, Ewn Harrison and Riinu Pius page 194

- Used for missing data identification

```{r}
finalfit::colon_s %>% 
  as_tibble()
```



