---
title: "Week 3: Hypthesis Testing (and alternatives)"
subtitle: ""
author: "<large>Charlotte Hadley</large>"
output:
  xaringan::moon_reader:
    css: 
      - "default"
      - "ninjutsu"
      - "css/lecture-styles.css" # You need to change this file path to css/...
      - "https://cdnjs.cloudflare.com/ajax/libs/animate.css/4.1.1/animate.min.css"
      - "assets/ninpo.css"
    chakra: "https://remarkjs.com/downloads/remark-latest.min.js"
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      beforeInit: "js/macros.js"
      countIncrementalSlides: false
---

class: split-two, with-thick-border border-black

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, servr.daemon = TRUE)
knitr::opts_chunk$set(cache=TRUE, autodep = TRUE, fig.retina = 3, message = FALSE, warning = FALSE)
library(tidyverse)
library(gt)
```

```{r, echo=FALSE, cache=FALSE}
xaringanExtra::use_progress_bar(color = "#e10020", location = "top", height = "5px")

# thanks to https://github.com/jvcasillas/xaringan_bib
source(here::here("static", "xaringan-bib.R"))
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "numeric", 
           cite.style = "numeric", 
           max.names = 1,
           dashed = TRUE)
bib <- ReadBib(here::here("static", "bibtex-file.bib"))
citet_charlie <- function(tag) {
  RefManageR::Citet(bib,
                    tag,
                    .opts = list(
                      bib.style = "numeric",
                      cite.style = "numeric",
                      max.names = 1
                    ))
}
```

---

# p-value notes

I'm dumping a bunch of useful stuff about p-values I found while writing Week 02 now.

## Twitter poll: same p-values different sizes

"If you have two studies with the *exact* same p-value, one with a small sample size and one with a large sample size, which would you find more convincing?"

- https://twitter.com/LucyStats/status/1029534591760195584?s=20&t=KE6HPh3zRy42IGvfu7Jp5g

And a GREAT follow-up article from the author https://livefreeordichotomize.com/2018/08/21/p-value-thoughts-a-twitter-follow-up/

Lucy D’Agostino McGowan follows up in 2022 with a great talk "What is the value of the p-value" (https://www.lucymcgowan.com/talk/north_carolina_translational_and_clinical_sciences_institute/) and the slides can be found here: https://docs.google.com/presentation/d/1W51xBJOG7C37vHLJuBR4WT6NCJXQN0Iah-NKk9VCLxg/edit#slide=id.p

Good tweet about what a p-value shows

```{r, eval=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Andy_Bloch/status/1469396978261913601?s=20&t=g3jbJvlH_ri3Qhjb4dq7qA")
```

# The perils of exporatory data analysis

https://darrendahly.github.io/post/2017-02-03-exploratory/








